\documentclass[12pt]{article}

\title{Bencozaham}
\author{
	Benjamin Karstad
	\texttt{- 101092172}
	\and
	Conor MacQuarrie
	\texttt{- 100824788}
	\and
	Zacharaia Maurice
	\texttt{- 101116412}
	\and
	Graham Shannon
	\texttt{- 100970902}
}

\begin{document}

\maketitle

\section*{Project Description}

Our project is a companion app that will help keep you organized when travelling.

\begin{itemize}

	\item{Checklist}

	The app will have a checklist of items that you packed.
	This makes it easier to know what you have and means that you won't forget to pack anything when you leave.
	You will also be able to load from common templates.
	If you're packing for a camping trip, the app will suggest items like a tent, sleeping bag, cooler etc.
	If you're packing for a beach vacation the app will suggest items like a bathing suit, sunglasses and sunscreen.
	You will be able to save your own templates to make packing for similar trips in the future easy.

	\item{Itinerary}

	This will allow you to schedule flights and any important events.
	You can choose to set reminders for these events, and the reminders can include any packed items you wish to bring.
	For example, your flight reminder may also remind you to have your passport.
	A reminder for a hike may remind you to bring your camera, hiking boots, and your water bottle.

	\item{Budgeting}

	This will allow you to give your entire trip a budget.
	This budget will be converted to the destination currency.
	This will give you an idea of how much money you can spend on your trip,
	while staying within your intended budget.
	You can also input a specific amount of currency.

	The user will also have access to a database of common goods/services and their approximate price in the destination country.
	This ensures that travellers know what they should be paying and can avoid being gouged by tourist traps.
\end{itemize}

Our app is interesting because it eases some of the stressful components of travelling.
It makes planning for packing easy.
It takes away the stress of not knowing whether you forgot something at your destination.
It lets you spend responsibly when you may not have a great perception of the value of local currency.
It helps you organize your daily events during your trip.

The project makes sense in a mobile form because most people tend to bring their mobile devices with them on vacation.
Alerting users with important information is also better on mobile devices;
since people tend to have their phone on them most of the day so they will see the alert promptly.

\section*{Functional Properties}

\section*{Non-Functional Properties}

\section*{User Scenarios}

\end{document}