\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage{subcaption}

\title{TripEase - Benconzaham}
\author{
Benjamin Karstad
\texttt{- 101092172}
\and
Conor MacQuarrie
\texttt{- 100824788}
\and
Zacharaia Maurice
\texttt{- 101116412}
\and
Graham Shannon
\texttt{- 100970902}
}

\begin{document}

	\maketitle

	\pagebreak

	\section*{Demo Description}

	\begin{itemize}

		\item{Packing Checklist}
		\begin{itemize}
			\item Add/Remove Items (real)
			\item Persistent Use (simulated)
		\end{itemize}

		\item{Itinerary/Planner}
		\begin{itemize}
			\item Add itinerary tasks with date & time (real)
			\item Persistent Use (real)
			\item Google Calendar Integration (to do)
		\end{itemize}

		\item{Budgeting}
			\begin{itemize}
				\item Currency Conversion (simulated)
				\item Budget Items (simulated)
				\item Price Database (to do)
			\end{itemize}

		\item{Misc Utilities}

		\begin{itemize}
			\item Weather
			\item Local emergency numbers
			\item Translation \& Common Phrases
		\end{itemize}

		\item{Offline Saving}

	\end{itemize}
	
	\section*{Difficulties}
	\begin{itemize}
		\item Integrating data with firebase for persistent use.
		\item Settling on tool to display lists.
		\item Connecting to Google Calendar to store itinerary data in the users calendar.
	\end{itemize}
	
	\section*{Plans For Next Month}
	\begin{itemize}
		\item Changing from ListView to RecyclerView, allowing a more customizable list.
		\item Integrating data with Firebase for persistent use.
		\item Allowing users to store and load item templates.
		\item Ability to delete data from the itinerary and update on firebase.
		\item Implement offline saving and local storage.
	\end{itemize}

\end{document}
